Characterizing edges in signed and vector-valued graphs

### 2017-12-18 cc/bias_directed.tex
typos and stability in cc
pass over CC

Having two parameters per node, one for outgoing edges and another one for incoming edges clearly
targets directed graphs. Many online interactions are inherently directed, for instance friendship,
trust or communication. On the other hand, predicting edge signs in undirected graphs is an equally
relevant objective. A prime example of such a situation is when we are given $n$ objects, some
pairwise similarities them, and the similarity function itself, which unfortunately takes an
exorbitant time to be evaluated. There is an underlying graph and being able to predict the sign of
its undirected edges would save us expensive evaluations of the symmetric similarity function.

A trivial way to turn an undirected graph $G$ into a directed graph $G'$ is to let $V'=V$ and, for
every edge $(u,v)$ in $E$, to add both \euv{} and \evu{} to $E'$ with the same sign as $(u,v)$. In
terms of our generative model, this corresponds to putting all the probability mass of $\mu$ on the
$p=q$ diagonal. This is clearly not a very satisfactory solution, for it removes one degree of
freedom from the model. To illustrate this point, we conduct the following experiment. We use our
previous \dssn{} datasets and remove the edge direction. As mentioned earlier, for few pairs of
nodes there are reciprocal edges of different signs, in which case we pick a sign arbitrarily. Given
those undirected graphs, we orient them using the approach described above and compare our method
with the \complowrank{} approach ran directly on the undirected graphs. This is a fair comparison,
for \complowrank{} is designed to works solely on undirected graphs.

As we can see in \autoref{tab:bias_exp_undir}, our methods perform worse than when running on the
original directed graphs. Looking at \uslpropGsec{} on a 15\% training set as an example, we observe
that the MCC decreases by one (\kiw{}) to almost ten (\epi{}) points. On the other hand, the
\complowrank{} seems to perform better. Recall however that because it is an undirected method in
the first place and because we roughly double the number of signed edges, a 15\% training size means
the algorithm gets to observe more signs and therefore perform better. This small experiment thereby
shows that although the performance remains decent, not having direction information hurt our bias.

>>>>

Having two parameters per node, one for outgoing edges and another one for incoming edges, clearly
targets directed graphs. Many online interactions are inherently directed, for instance friendship,
trust or communication. On the other hand, predicting edge signs in undirected graphs is an equally
relevant objective. A prime example of such a situation is when we are given $n$ objects, some
pairwise similarities them, and the similarity function itself, which unfortunately takes an
exorbitant time to be evaluated. There is an underlying graph and being able to predict the sign of
its undirected edges would save us expensive evaluations of the symmetric similarity function.

A trivial way to turn an undirected graph $G$ into a directed graph $G'$ is to let $V'=V$ and, for
every edge $(u,v)$ in $E$, to add both \euv{} and \evu{} to $E'$ with the same sign as $(u,v)$. In
terms of our generative model, this corresponds to putting all the probability mass of $\mu$ on the
$p=q$ diagonal. This is clearly not a very satisfactory solution, for it removes one degree of
freedom from the model. To illustrate this point, we conduct the following experiment. We use our
previous \dssn{} datasets and remove the edge direction. As mentioned earlier, for a few pair of
nodes, there are reciprocal edges of different signs, in which case we pick a sign arbitrarily. Given
those undirected graphs, we orient them using the approach described above and compare our method
with the \complowrank{} approach ran directly on the undirected graphs. This is a fair comparison,
for \complowrank{} is designed to works solely on undirected graphs.

As we can see in \autoref{tab:bias_exp_undir}, our methods perform worse than when running on the
original directed graphs. Looking at \uslpropGsec{} on a 15\% training set as an example, we observe
that the MCC decreases by one (\kiw{}) to almost ten (\epi{}) points. On the other hand, the
\complowrank{} seems to perform better. Recall however that because it is an undirected method in
the first place and because we roughly double the number of signed edges, a 15\% training size means
the algorithm gets to observe more signs and therefore perform better. This small experiment thereby
shows that although the performance remains decent, not having direction information hurts our bias.

### 2017-12-18 cc/bias_main.tex
move social balance to first section
typos and stability in cc
pass over CC

Let us recall first the sign model we used for \dssn{}. Each node $u$ is endowed with two parameters
$p_u$ and $q_u$ drawn from an arbitrary joint distribution $\mu$ over $[0,1]\times [0,1]$. $p_u$ can be
interpreted as the tendency of $u$ to send positive edges to other nodes (\ie{} the
\enquote{niceness} of $u$), while $q_u$ can be interpreted as the tendency of $u$ to receive positive
edges from other nodes (\ie{} the \enquote{popularity} of $u$). The sign of an edge \euv{} is then
chosen to be positive with probability $\frac{p_u+q_v}{2}$. This suggests that nodes in the
graph have a form of agency, and this imposes that edges are directed. We show experimentally that
failing to meet these two assumptions harms the performance of our previous method. This is not
surprising, for our bias is no more justified in that case. Therefore, we suggest a different bias,
drawing heavily on social balance theories, although we shall see later this holds for many
nonsocial graphs as well.

@@

>>>>

Let us recall first the sign model we used for \dssn{}. Each node $u$ is endowed with two parameters
$p_u$ and $q_u$ drawn from an arbitrary joint distribution $\mu$ over $[0,1]\times [0,1]$. $p_u$ can be
interpreted as the tendency of $u$ to send positive edges to other nodes (\ie{} the
\enquote{niceness} of $u$), while $q_u$ can be interpreted as the tendency of $u$ to receive positive
edges from other nodes (\ie{} the \enquote{popularity} of $u$). The sign of an edge \euv{} is then
chosen to be positive with probability $\frac{p_u+q_v}{2}$. This suggests that nodes in the
graph have a form of agency, and further imposes that edges are directed. We show experimentally that
failing to meet these two assumptions harms the performance of our previous methods. This is not
surprising, for our bias is no more justified in that case. Therefore, we suggest a different bias,
drawing heavily on social balance theories, although we shall see later this holds for many
nonsocial graphs as well.

@@

\subsection{Social balance as a learning bias}
\label{sub:bias_balance}

\input{bias_balance}

### 2017-12-18 cc/bias_model.tex
pass over CC

Namely, we consider \emph{gene regulatory networks}. The nodes of such directed graphs are various
chemicals (such as genes, proteins or messenger RNAs) and a directed edge \euv{} indicates that one
node $u$ influences the concentration of another node $v$ through a chemical reaction. This
influence can be positive (that is, an increase of $u$ concentration results in an increase of $v$
concentration) or negative (that is, an increase of $u$ concentration results in a decrease of $v$
concentration). In this context, we could now interpret the \enquote{niceness} of $u$ as it ability
to accelerate chemical reactions, and its \enquote{popularity} as its propensity to take part in
reactions accelerated by other nodes. Intuitively, this is quite far-fetched. To demonstrate this,
we borrow the following three gene regulatory networks from \autocite[Table 1]{BioSigned09}, and
display their statistics in \autoref{tab:bias_bio_dataset}:
\begin{enumerate}[1.]
  \item The signaling pathways of the \hip{} CA1 neuron~\autocite{Hippocamp05}.
  \item The interactions between genes and their products that are involved in \can{} development in
    humans and mouses~\autocite{Cancer07}.
  \item The \reg{} database\autocite{RegulonDB16}, summarizing the connection between transcription
    factors and their targets in the Escherichia coli K-12 bacteria. We download four
    files\footnote{\url{http://regulondb.ccg.unam.mx/menu/download/datasets/index.jsp}} containing
    experimental evidence and keep only the positive and negative edges with \textsf{Strong}
    support.
\end{enumerate}
%\url{http://causalbionet.com/}

@@

Compared with the \dssn{} of the previous chapter, those biological are smaller, have lower average
degree and little to no reciprocal edges. Trying to solve the \esp{} problem using the same
procedure as in \autoref{s:exp}, we read in \autoref{tab:cc_bio_exp} that our methods have lower
absolute MCC performance (for instance, \uslpropGsec{} with a 15\% training size achieves $20$, $24$
and $45$ compared with values between $36$ and $61$ on \dssn{}).  To further illustrate the mismatch
between the troll bias and biological networks, notice that the standard deviation figures are
several times larger than those reported in \autoref{tab:all_mcc}.

>>>>

Namely, we consider \emph{gene regulatory networks}. The nodes of such directed graphs are various
chemicals (such as genes, proteins or messenger RNAs) and a directed edge \euv{} indicates that one
node $u$ influences the concentration of another node $v$ through a chemical reaction. This
influence can be positive (that is, an increase of $u$ concentration results in an increase of $v$
concentration) or negative (that is, an increase of $u$ concentration results in a decrease of $v$
concentration). In this context, we could now interpret the \enquote{niceness} of $u$ as it ability
to accelerate chemical reactions, and its \enquote{popularity} as its propensity to take part in
reactions accelerated by other nodes. Intuitively, this is quite far-fetched. To demonstrate this,
we borrow the following three gene regulatory networks from \autocite[Table 1]{BioSigned09}, and
display their statistics in \autoref{tab:bias_bio_dataset}:
\begin{enumerate}[1.]
  \item The signaling pathways of the \hip{} CA1 neuron~\autocite{Hippocamp05}.
  \item The interactions between genes and their products that are involved in \can{} development in
    humans and mouses~\autocite{Cancer07}.
  \item The \reg{} database~\autocite{RegulonDB16}, summarizing the connection between transcription
    factors and their targets in the Escherichia coli K-12 bacteria. We download four
    files\footnote{\url{http://regulondb.ccg.unam.mx/menu/download/datasets/index.jsp}} containing
    experimental evidence and keep only the positive and negative edges with \textsf{Strong}
    support.
\end{enumerate}
%\url{http://causalbionet.com/}

@@

Compared with the \dssn{} of the previous chapter, those biological networks are smaller, have lower average
degree and little to no reciprocal edges. Trying to solve the \esp{} problem using the same
procedure as in \autoref{s:exp}, we read in \autoref{tab:cc_bio_exp} that our methods have lower
absolute MCC performance (for instance, \uslpropGsec{} with a 15\% training size achieves $20$, $24$
and $45$ compared with values between $36$ and $61$ on \dssn{}).  To further illustrate the mismatch
between the troll bias and biological networks, notice that the standard deviation figures are
several times larger than those reported in \autoref{tab:all_mcc}.

### 2017-12-18 cc/cc_non_worst_case.tex
pass over CC

We now look at two settings where our bias is likely to be present.  In the first one, we assume the
input graph is randomly perturbed version of a consistent clustering. In the second one, we do not
assume anything about such a consistent clustering but expect instead that the optimal solution is
\enquote{clear} enough that it does not change when weights are multiplicatively perturbed.

@@

As we have seen, assuming the Unique Games Conjecture, the \mmc{} problem, and therefore
the \pcc{} problem on a general graph, cannot be approximated to within a constant factor in the worst
case.  But maybe we can do better in the average case, which motivates the study of semi-random
model, where real graphs are seen as being obtained from the controlled perturbation of a perfectly
clusterable graph. In the simplest case, each edge sign is independently flipped with probability
$p \in [0, \shalf)$. This situation on complete graphs was considered in \autocite[Section
6]{Bansal2002}, showing a simple algorithm that with high probability makes
$\tilde{O}(n^\frac{3}{2})$ mistakes, and in \autocite[Theorem 2.6]{Ben-Dor99}, with an algorithm
recovering with high probability the planted partition of an unweighted graph in $O(n^2(\log n)^c)$,
where $c$ depends on the size of the smallest cluster and the noise probability.

\Textcite{Joachims2005} analyze a more refined weighted model, where weights are generated by a
probability distribution whose mean on true positive edges is larger than $\mu^+>0$ and whose mean
on true negative edges is smaller than $\mu^-<0$. They give a finite-sample bound on the number of
nodes misclustered w.r.t the planted partition as a function on the probability distribution
parameters. Indeed, as pointed out by \textcite{plantedAilon09}, independent and uniform noise is
not a good model of real situations, where the input of \pcc{}, \ie{} the similarity between nodes,
is often the result of a preprocessing, which may present strong correlations. Therefore, instead of
measuring the quality of a solution against the input (\ie{} the similarity information), they
argue it is more sensible to measure it against the (unknown) true optimal clustering that gave rise
to the input, and show that \ccpivot{} allows this, thanks to a new analysis. \Textcite{Mathieu2010}
also consider an adversarial model, where all edges are flipped with probability $p$ but the
adversary then decides whether to reveal the true sign or the flipped sign. On complete unweighted
graphs, they find a solution of \mind{} at most $1 + O(n^{-\nicefrac{1}{6}})$ times the optimal
whenever $p \leq \shalf - n^{-\nicefrac{1}{3}}$ by rounding the usual SDP solution. If, in addition,
there is no adversary, $p\leq\nicefrac{1}{3}$ and each planted cluster has at least
$\Theta(\sqrt{n})$ nodes, then the planted partition can be recovered exactly.
\Textcite{Makarychev2014} study the same adversarial model but on general weighted graphs, giving a PTAS
for \mind{} when $p\leq \nicefrac{1}{4}$. Under additional assumptions on the density of edges, they
present another algorithm that finds the ground truth clustering with an arbitrarily small
classification error.
% \footnote{They also mention a potentially interesting related work~\autocite{unobservedCC14}.}
% http://www.jmlr.org/papers/v15/chen14a.html
% \textcite{Noisy2CCLocality16} study the recovery of an arbitrary planted 2-partition under noisy
% measurement in special kind of graphs where each node is connected with a local neighborhood and
% show computationally efficient algorithms that only query an information theoretically optimal
% number of pair. I think it was extended in \url{https://doi.org/10.1109/TIT.2016.2600566}

@@

Whereas clustering objective functions are \NPh{} to optimize, we expect meaningful instances
in which we are interested to have additional structure which allows for guaranteed polynomial time
algorithms. We refer the reader to a critical overview~\autocite{clusteringFeasibility15} of some
such notions of structure proposed recently. Informally, a general idea is that the clustering should not
change (or at least very little) if the data are slightly perturbed. For instance, a weighted graph
is \emph{$\alpha$-stable} (with $\alpha>1$) for some partition objective if its optimal partition
remains the same whenever every weight $w_i$ is multiplied by a factor $c_i$ between $1$ and
$\alpha$.
Another notion is the $(c, \epsilon)$-approximation stability. Formally, a dataset $X$ is $(c,
\epsilon)$-stable if, for an objective function $\Phi$, any clustering whose cost is within a factor
$c$ of the optimal cost $OPT_{\Phi}$ is $\epsilon$-close to the optimal clustering (as measured by
the fraction of points in which the two clustering disagree). When the objective is \mind{} on
complete graphs, \textcite{StableCC09} show that for $(1+\alpha, \epsilon)$-instances, the
approximation algorithms we describe in \autoref{ssub:cc_harness_approx} find a solution that is
$(\nicefrac{49}{\alpha} + 1)\epsilon$ close to the optimal clustering.

>>>>

We now look at two settings where our bias is likely to be present.  In the first one, we assume the
input signs are randomly perturbed of an initial assignment derived from a consistent clustering. In the second one, we do not
assume anything about such a consistent clustering but expect instead that the optimal solution is
\enquote{clear} enough that it does not change when weights are multiplicatively perturbed.

@@

As we have seen, assuming the Unique Games Conjecture, the \mmc{} problem, and therefore
the \pcc{} problem on a general graph, cannot be approximated to within a constant factor in the worst
case.  But maybe we can do better in the average case, which motivates the study of semi-random
model, where real graphs are seen as being obtained from the controlled perturbation of a perfectly
clusterable graph. In the simplest case, each edge sign is independently flipped with probability
$p \in [0, \shalf)$. This situation on complete graphs was considered in \autocite[Section
6]{Bansal2002}, showing a simple algorithm that with high probability makes
$\tilde{O}(n^\frac{3}{2})$ mistakes, and in \autocite[Theorem 2.6]{Ben-Dor99}, with an algorithm
recovering with high probability the planted partition of an unweighted graph in $O(n^2(\log n)^c)$,
where $c$ depends on the size of the smallest cluster and on the noise probability.

\Textcite{Joachims2005} analyze a more refined weighted model, where weights are generated by a
probability distribution whose mean on true positive edges is larger than $\mu^+>0$ and whose mean
on true negative edges is smaller than $\mu^-<0$. They give a finite-sample bound on the number of
nodes misclustered w.r.t the planted partition as a function on the probability distribution
parameters. Indeed, as pointed out by \textcite{plantedAilon09}, uniform and independent noise is
not a good model of real situations, where the input of \pcc{}, \ie{} the similarity between nodes,
is often the result of a preprocessing, which may present strong correlations. Therefore, instead of
measuring the quality of a solution against the input (\ie{} the similarity information), they
argue it is more sensible to measure it against the (unknown) true optimal clustering that gave rise
to the input, and show that \ccpivot{} allows this, thanks to a new analysis. \Textcite{Mathieu2010}
also consider an adversarial model, where all edges are flipped with probability $p$ but the
adversary then decides whether to reveal the true sign or the flipped sign. On complete unweighted
graphs, they find a solution of \mind{} at most $1 + O(n^{-\nicefrac{1}{6}})$ times the optimal
whenever $p \leq \shalf - n^{-\nicefrac{1}{3}}$ by rounding the usual SDP solution. If, in addition,
there is no adversary, $p\leq\nicefrac{1}{3}$ and each planted cluster has at least
$\Theta(\sqrt{n})$ nodes, then the planted partition can be recovered exactly.
\Textcite{Makarychev2014} study the same adversarial model but on general weighted graphs, giving a PTAS
for \mind{} when $p\leq \nicefrac{1}{4}$. Under additional assumptions on the density of edges, they
present another algorithm that finds the ground truth clustering with an arbitrarily small
classification error.
% \footnote{They also mention a potentially interesting related work~\autocite{unobservedCC14}.}
% http://www.jmlr.org/papers/v15/chen14a.html
% \textcite{Noisy2CCLocality16} study the recovery of an arbitrary planted 2-partition under noisy
% measurement in special kind of graphs where each node is connected with a local neighborhood and
% show computationally efficient algorithms that only query an information theoretically optimal
% number of pair. I think it was extended in \url{https://doi.org/10.1109/TIT.2016.2600566}

@@

Whereas clustering objective functions are \NPh{} to optimize, we expect meaningful instances
in which we are interested to have additional structure which allows for guaranteed polynomial time
algorithms. We refer the reader to a critical overview~\autocite{clusteringFeasibility15} of some
such notions of structure proposed recently. Informally, a general idea is that the clustering should not
change (or at least very little) if the data are slightly perturbed. For instance, a weighted graph
is \emph{$\alpha$-stable} (with $\alpha>1$) for some partition objective if its optimal partition
remains the same whenever every weight $w_i$ is multiplied by a factor $c_i$ between $1$ and
$\alpha$.
Another notion is the $(c, \epsilon)$-approximation stability. Formally, a dataset $X$ is $(c,
\epsilon)$-stable if, for an objective function $\Phi$, any clustering whose cost is within a factor
$c$ of the optimal cost $OPT_{\Phi}$ is $\epsilon$-close to the optimal clustering (as measured by
the fraction of points on which the two clusterings disagree). When the objective is \mind{} on
complete graphs, \textcite{StableCC09} show that for $(1+\alpha, \epsilon)$-instances, the
approximation algorithms we describe in \autoref{ssub:cc_harness_approx} find a solution that is
$(\nicefrac{49}{\alpha} + 1)\epsilon$ close to the optimal clustering.

### 2017-12-18 cc/cc_problem_and_esp.tex
pass over CC

\esp{} can clearly be casted as a supervised classification problem where, given a labelled training
set of $m_0$ edges $\mathcal{X}=\{(e_1, y_1), \ldots, (e_{m_0}, y_{m_0})\}$, we can extract for
every edge a feature vector in $\Rbb^d$, pick an hypothesis class like linear models, find among
this class the hypothesis minimizing the empirical risk, and use it to predict the sign of edges in
the testing set. In contrast, \pcc{} in an agnostic problem. More precisely, the hypothesis class is
fixed, as it consists of all possible partitions of the nodeset. We are trying to find the partition
that best approximates the observed signs, but each weakly unbalanced cycle is gonna cost us at
least one unavoidable mistake. Despite this fundamental difference in their nature, \pcc{} is
connected with \esp{} at two levels, theoretical and practical. On the theoretical side, computing
the minimum number of disagreements gives a measure of the \esp{} problem complexity.  Intuitively,
given a labelled subgraph $H$ of $G$ (that is the training set), if there are few disagreements, the
\enquote{quasi} connected components of $H^+$ should give a reasonable estimation of the underlying
consistent clustering. Predicting the signs based on this clustering should results in few errors.
More formally, one can show that by finding a clustering $\cluster^\star$ of $H$ that has less
disagreements than $\kappa$ times the smallest number of disagreements $\Delta$, the number of
errors on the testing set will be at most of order $\kappa\Delta + \sqrt{mn\log
n}$~\autocite[Theorem 6]{Cesa-Bianchi2012b}. These theoretical considerations naturally lead to
practical a batch algorithm, which first finds a clustering minimizing as much as possible the number
of disagreements on the training set and then predicts signs according to this clustering. Our
assumption in doing so is that, according to our bias, our graph has few disagreements. Therefore,
provided we can find a clustering close to the optimal, we will not make too many prediction
mistakes.

@@

Furthermore, as mentioned in the introduction of this thesis \vpageref{sub:intro_signed_graphs},
\pcc{} have been used in many
domains. For instance in computer vision, it is used to segment images in
2D~\autocites{Kim2011}{Bagon2011}{CellSeg14} or 3D~\autocites{VolumeSegmentation12}{Beier2015}, to
simplify 3D shapes~\autocite{Shape3D17} and to track target across sequential video
frames~\autocite{multiTracking15}. When the nodes are words, \pcc{} is employed to identify
coreference~\autocites{graphicalCoreference04}{Elsner2009} or cluster synonym
words~\autocite{SignedWordRatings}. It plays a large role in biology, to clusters
genes~\autocite{Ben-Dor99}, identify mutation regions in chromosomes~\autocite{Das2015} or finding
stable subsystems~\autocite{monotoneBiology07}. Applied to social networks, it helps analyze
political assemblies~\autocites{Mendonca2015}{Jiang2015}{BrazilCC17} and international
relations~\autocites{Traag2009}{CommunityUN12}. Finally, given large databases with duplicated
records, it naturally models entity
resolution~\autocites{Crosslingual07}{DeDup09}{LargeScaleDeDup09}{WeightedER14}.

>>>>

\esp{} can clearly be casted as a supervised classification problem where, given a labelled training
set of $m_0$ edges $\mathcal{X}=\{(e_1, y_1), \ldots, (e_{m_0}, y_{m_0})\}$, we can extract for
every edge a feature vector in $\Rbb^d$, pick an hypothesis class like linear models, find among
this class the hypothesis minimizing the empirical risk, and use it to predict the sign of edges in
the testing set. In contrast, \pcc{} in an agnostic problem. More precisely, the hypothesis class is
fixed, as it consists of all possible partitions of the nodeset. We are trying to find the partition
that best approximates the observed signs, but each weakly unbalanced cycle will cost us at
least one unavoidable mistake. Despite this fundamental difference in their nature, \pcc{} is
connected with \esp{} at two levels, theoretical and practical. On the theoretical side, computing
the minimum number of disagreements gives a measure of the \esp{} problem complexity.  Intuitively,
given a labelled subgraph $H$ of $G$ (that is the training set), if there are few disagreements, the
\enquote{quasi} connected components of $H^+$ should give a reasonable estimation of the underlying
consistent clustering. Predicting the signs based on this clustering should results in few errors.
More formally, one can show that by finding a clustering $\cluster^\star$ of $H$ that has less
disagreements than $\kappa$ times the smallest number of disagreements $\Delta$, the number of
errors on the testing set will be at most of order $\kappa\Delta + \sqrt{mn\log
n}$~\autocite[Theorem 6]{Cesa-Bianchi2012b}. These theoretical considerations naturally lead to
a practical batch algorithm, which first finds a clustering minimizing as much as possible the number
of disagreements on the training set and then predicts signs according to this clustering. Our
assumption in doing so is that, according to our bias, our graph has few disagreements. Therefore,
provided we can find a clustering close to the optimal, we will not make too many prediction
mistakes.

@@

Furthermore, as mentioned in the introduction of this thesis \vpageref{sub:intro_signed_graphs},
\pcc{} have been used in many
domains. For instance in computer vision, it is used to segment images in
2D~\autocites{Kim2011}{Bagon2011}{CellSeg14} or 3D~\autocites{VolumeSegmentation12}{Beier2015}, to
simplify 3D shapes~\autocite{Shape3D17} and to track targets across sequential video
frames~\autocite{multiTracking15}. When the nodes are words, \pcc{} is employed to identify
coreference~\autocites{graphicalCoreference04}{Elsner2009} or cluster synonym
words~\autocite{SignedWordRatings}. It plays a large role in biology, to clusters
genes~\autocite{Ben-Dor99}, identify mutation regions in chromosomes~\autocite{Das2015} or finding
stable subsystems~\autocite{monotoneBiology07}. Applied to social networks, it helps analyze
political assemblies~\autocites{Mendonca2015}{Jiang2015}{BrazilCC17} and international
relations~\autocites{Traag2009}{CommunityUN12}. Finally, given large databases with duplicated
records, it naturally models entity
resolution~\autocites{Crosslingual07}{DeDup09}{LargeScaleDeDup09}{WeightedER14}.
